\subsection{Outlines from Cecil Holcombe}

\subsubsection{God's Portrait of Motherhood}
\index[speaker]{Cecil Holcombe!Proverb 31 (God's Portrait of Motherhood)}
\index[series]{Proverbs (Cecil Holcombe)!Pro 31:10-31 (God's Portrait of Motherhood)}
\index[event]{Mothers' Day!Proverb 31:10-31 (Cecil Holcombe) - God's Portrait of Motherhood)}
\index[date]{2014/05/10!Proverbs 31:10-31 (God's Portrait of Motherhood) (Cecil Holcombe)}

\begin{compactenum}[I.]
    \item Her \textbf{Cost}  v 10 - “Who can find a virtuous woman? for her price is far above rubies.”
 	\item Her \textbf{Characteristics}  v 10 - “Who can find a virtuous woman? for her price is far above rubies.”
   \begin{compactenum}[A.]
    	\item SHE IS TRUSTWORTHY  vv 11-12  - “The heart of her husband doth safely trust in her, so that he shall have no need of spoil. {12} She will do him good and not evil all the days of her life.”
    	\item SHE IS INDUSTRIOUS  vv 13-14 - “She seeketh wool, and flax, and worketh willingly with her hands. {14} She is like the merchants' ships; she bringeth her food from afar.”   v 19 - “She layeth her hands to the spindle, and her hands hold the distaff.”  v 27 - “She looketh well to the ways of her household, and eateth not the bread of idleness.”
    	\item SHE IS COMPASSIONATE  v 15 - “She riseth also while it is yet night, and giveth meat to her household, and a portion to her maidens.”
    	\item SHE IS HEALTH CONSCIOUS  v 17 - “She girdeth her loins with strength, and strengtheneth her arms.”
    	\item SHE IS SOUND IN JUDGMENT  v 16 - “She considereth a field, and buyeth it: with the fruit of her hands she planteth a vineyard.”
 v 18 - “She perceiveth that her merchandise is good: her candle goeth not out by night.”
    	\item SHE IS GENEROUS  v 20 - “She stretcheth out her hand to the poor; yea, she reacheth forth her hands to the needy.”
    	\item SHE IS PRUDENT  v 21 - “She is not afraid of the snow for her household: for all her household are clothed with scarlet.”
    	\item SHE IS FASHIONABLE  v 22-24 - “She maketh herself coverings of tapestry; her clothing is silk and purple. {23} Her husband is known in the gates, when he sitteth among the elders of the land. {24} She maketh fine linen, and selleth it; and delivereth girdles unto the merchant.”
    	\item SHE IS KIND  v 26 - “She openeth her mouth with wisdom; and in her tongue is the law of kindness.”
    \end{compactenum}
   \item Her \textbf{Compensation}  v 10 - “Who can find a virtuous woman? for her price is far above rubies.”
   \begin{compactenum}[A.]
    	\item BY HER KIDS
 v 28a “Her children arise up, and call her blessed”
    	\item BY HER COMPANION
 v 29b “her husband also . . . praiseth her.”
    	\item  BY HER COMMUNITY
 v 31 - “Give her of the fruit of her hands; and let her own works praise her in the gates”
    	\item BY HER KING
 vv 29-30 “Many daughters have done virtuously, but thou excellest them all. {30} Favour is deceitful, and beauty is vain: but a woman that feareth the LORD, she shall be praised.”
 v 25b - “. . . she shall rejoice in time to come.
    \end{compactenum}

\end{compactenum}

\index[FACEBOOK]{FUNDAMENTAL BAPTIST SERMON OUTLINES!Cecil Holcombe - Proverb 31:10-31!2015/05/10}
