\subsection{Outlines from Clarence Billheimer}


\subsubsection{Characteristics of a Faithful Christian}

\index[speaker]{Clarence Billheimer!Proverb 30:24-28 (Characteristics of a Faithful Christian)}
\index[series]{Proverbs (Clarence Billheimer)!Pro 30:24-28 (Characteristics of a Faithful Christian)}
\index[date]{2020/09/02!Proverb 30:24-28 (Characteristics of a Faithful Christian) (Clarence Billheimer)}

\noindent  \textbf{Introduction: } You might wonder why I chose this text for a message. It’s one of the observations of life and nature that the inspired writer of Proverbs noticed. That’s the reason I chose it. As the writer looked at these creations of God, he noticed some things about them which God created within them that we can apply to our lives if we want to be faithful, and be in a way like these creatures. They would not survive without the instincts God gave them, and we can’t be faithful if we lack the like characteristics.\\
\\
\begin{compactenum}[I.]
    \item The dedication of the ant
    \begin{compactenum}[A.]
	    \item A people not strong
	    \item Prepares for the future
	    \item Procures his need with diligence
	    \item Application—we don’t need a lot of strength to be prepared and diligent.
	\end{compactenum}
    \item The dependence of the coney
    \begin{compactenum}[A.]
	    \item Realizes his feebleness
	    \item Runs to the rocks for shelter and safety
	    \item Receives needed protection
	    \item Application—we need to depend on God and build on the Rock, Christ Jesus.
		\end{compactenum}
    \item The determination of the locust
    \begin{compactenum}[A.]
	    \item Working together
	    \item Wreaking havoc
	    \item Weaken what they consume
	    \item Application—we need to work together to accomplish the complete mission God gave us.
		\end{compactenum}
    \item The delicacy of the spider
    \begin{compactenum}[A.]
	    \item Found in festive places
	    \item Found in family placed
	    \item Feared by his prey
	    \item Application—Jesus said, “Be wise as serpents and harmless as doves.”\\
	\end{compactenum}
\end{compactenum}

\noindent  \textbf{Conclusion: } A Christian will be most faithful to God when he’s dedicated to Him, dependent on Him, determined for Him, and delicate in his behavior so he’s not an offense or stumbling block.


\index[FACEBOOK]{FUNDAMENTAL BAPTIST SERMON OUTLINES!Clarence Billheimer - Proverb 30:24-28!2020/09/02}

