\section{Psalm 30 Outlines}

\subsection{My Outlines}

\subsubsection{God's Favour}
\index[speaker]{Keith Anthony!Psalm 030 (God's Favour)}
\index[series]{Psalms (Keith Anthony)!Psalm 030 (God's Favour)}
\index[date]{2014/11/02!Psalm 030 (God's Favour) (Keith Anthony)}
Introduction: The superscription for Psalm 30 reads ``A Psalm and Song at the dedication of the house of David,'' connecting it with the dedication of the site for the Temple (\index[scripture]{1 Chronicles!1Chr 21:26}1 Chronicles 21:26 and \index[scripture]{1 Chronicles!1Chr 22: 1}1 Chronicles 22:1). The psalm has three verses (\index[scripture]{Psalms!Psa 030:02}Psalm 30:2, \index[scripture]{Psalms!Psa 030:08}Psalm 30:8, and \index[scripture]{Psalms!Psa 030:10}Psalm 30:10) with 13 words, showing that despite David's sin and deep-down rebellion, God still kept His covenant with David. Instances of the number 13 typically indicate rebellion, or an opportunity to choose between rebellion or obedience, or here, repentance. Psalm 30:3 indicates that God had delivered David, at some point, from the brink of death. Some hold that Psalm 30:6-7 refers to the plague God sent in response to David's census, done against God's command (see 2 Samuel 24 and 1 Chronicles 21). Consider aspects of God's favor upon David:
\begin{compactenum}
    \item David was spared at the \textbf{Brink of Death} \index[scripture]{Psalms!Psa 030:03} (Psa 30:3)
    \item God's favor was David's \textbf{Basis for Deliverance} \index[scripture]{Psalms!Psa 030:05} (Psa 30:5)
    \item God's favor was given despite David's \textbf{Bad Declaration} - David was comfortable and secure and apparently forgot the source of all his blessings. \index[scripture]{Psalms!Psa 030:06} (Psa 30:6)
    \item God's seeming absence results in David's \textbf{Better Decision}  \index[scripture]{Psalms!Psa 030:07} (Psa 30:7)
    \item Because of God's favor David gets \textbf{Blessing instead of Dust} \index[scripture]{Psalms!Psa 030:09} (Psa 30:9)
    \item God changed David's \textbf{Bitterness into Dancing} \index[scripture]{Psalms!Psa 030:11} (Psa 30:11)
    \item Because of God's Favor, David has a \textbf{Bright Destiny} \index[scripture]{Psalms!Psa 030:12} (Psa 30:12)\\
\end{compactenum}
Do you have God's favor in your life? Do you even want it?

% made 3 (1, 7, 8)  may 2 (5, 12)  me 7 (1 (2x), 2, 3, 10, 11 (2x)) mercy 1 (10) moment 1 (5) morning 1(5) mountain 1 (7)  mourning 1 (11) moved 1 (6) my 10 (1, 2, 3, 6, 7, 9, 10, 11 (2x), 12) 