\subsection{Outlines from Brian Eades}

\subsubsection{Lord Be Thou My Helper}

\index[speaker]{Brian Eades!Psalm 030 (Lord Be Thou My Helper)}
\index[series]{Psalms (Brian Eades)!Psalm 030 (Lord Be Thou My Helper)}
\index[date]{2021/01/03!Psalm 030 (Lord Be Thou My Helper) (Brian Eades)}
\textbf{Introduction: }There was an old Charlie Daniels song that said, "I ain't asking nobody for Nothin, if I can't get it on my own". Many of us have the attitude we are going to do it all ourselves without asking for Holy intervention. David said in one place "I will lift up mine eyes unto the hills from whence cometh my help, my help comes from the Lord who made Heaven and Earth".\\

\begin{compactenum}
    \item GOD CAN HELP YOU WITH LONELINESS
    \item GOD CAN HELP YOU WITH LOSS
    \item GOD CAN HELP YOU WITH LIBERATION
    \item GOD CAN HELP YOU WITH LOVE
    \item GOD CAN HELP YOU WITH LOOT
    \item GOD CAN HELP YOU WHEN YOU ARE LOST
    \item GOD CAN HELP YOU WITH LIFE ABUNDANTLY
    \item GOD CAN HELP YOU GET LOOSE FROM ADDICTIONS
\end{compactenum}


\index[FACEBOOK]{SERMON HINTS!Brian Eades (Lord Be Thou My Helper) - Psalm 30!2021/01/03}


\subsubsection{We Will Not Cry Forever}

\index[speaker]{Brian Eades!Psalm 030 (Lord Be Thou My Helper)}
\index[series]{Psalms (Brian Eades)!Psalm 030 (We Will Not Cry Forever)}
\index[date]{2018/04/30!Psalm 030 (We Will Not Cry Forever) (Brian Eades)}
\textbf{Introduction: }We are told in this all famous song that weeping may endure for a night but joy comes in the morning. I got up this morning to a bright sunshine on a cool fall day. It's a happy day for me. My children are both grown up and healthy and happily married with successful jobs. My granddaughter is healthy and me and my wife have lived the American dream. But I also know that night is coming and there will be tears because it cannot last in this world. Statistically the average person will shed 16.907 gallons of tears in their lifetime!  But there is a glad morning when there will be no darkness to ever fall for God's people.\\

\begin{compactenum}
    \item THE AWFULNESS OF TEARS (Job)
    \item THE ACQUIREMENT OF TEARS
Psalms 56:8 (KJV)  Thou tellest my wanderings: put thou my tears into thy bottle: are they not in thy book?
    \item THE ABSENCE OF TEARS
Isaiah 25:8 (KJV)  He will swallow up death in victory; and the Lord GOD will wipe away tears from off all faces; and the rebuke of his people shall he take away from off all the earth: for the LORD hath spoken it.
\end{compactenum}


\index[FACEBOOK]{SERMON HINTS!Brian Eades (We Will Not Cry Forever) - Psalm 30!2018/04/30}


\subsubsection{Girded with Gladness}

\index[speaker]{Brian Eades!Psalm 030 (Girded with Gladness)}
\index[series]{Psalms (Brian Eades)!Psalm 030 (Girded with Gladness)}
\index[date]{2018/04/30!Psalm 030 (Girded with Gladness) (Brian Eades)}
\textbf{Introduction: }Here the song writer states the fact that God has clothed him with gladness. This is not loose fitting clothes, but it is something girded upon him. It is buckled down tight and rapped about him. One person has said that happiness is like the surface of the ocean that changes with the tide and can be affected by the winds and storm, however Joy and inner gladness is like the still calm of the bottom of the ocean that is unaffected by the elements.\\

\begin{compactenum}
    \item THE PERISHING CLOTHED
Genesis 3:21 (KJV)  Unto Adam also and to his wife did the LORD God make coats of skins, and clothed them.
    \item THE PRODIGAL CLOTHED
We remember the prodigal coming home with his apologies only to be wrapped about with a new robe and then celebrated with a great party. We could say that he is girded with gladness.
    \item THE PITIFUL CLOTHED
In the story of the demoniac, he went from being a miserable soul to being sitting and clothed and in his right mind.
    \item THE PENITENT CLOTHED
Revelation 3:18 (KJV)  I counsel thee to buy of me gold tried in the fire, that thou mayest be rich; and white raiment, that thou mayest be clothed, and that the shame of thy nakedness do not appear; and anoint thine eyes with eyesalve, that thou mayest see.
\end{compactenum}


\index[FACEBOOK]{SERMON HINTS!Brian Eades (Girded with Gladness) - Psalm 30!2018/04/30}